\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}

\title{GAM130 - Team 2 - Sprint 2 Plan}
\author{Aventale Interactive}
\date{14/02/20 - 28/02/20}

\begin{document}
\maketitle

\newpage
\section{Brief Overview}
The plan for this sprint is to start integrating features to start forming an actual game prototype which you can start to see take form. From the programming perspective it is intended to have the movement and pathfinding integrated as one which would allow for the movement to be completed as a mechanic. It is also intended for the health system to be started to then lead on to the combat which will allow us to get a feel for the game a bit more. There will also be some minor refactoring to reduce patching in the future. An input handler and unit creation kit will be created to allow the creation of units and for input to be entered by the designers.
\\\\
From the perspective of the modellers, it is intended for most of the required environment models that are interactable to be produced to allow us to implement them into the scene to start allowing the game to start taking shape. Furthermore, it is also expected for the regular cat blockout to be complete, so that the animator is able to start rigging in the future.
\\\\
The artist intends to start producing the concept art for the archers and spearman to allow the modellers to model them respectively in the future to ensure there are no blockers. Furthermore, concept art for a plushie will also be produced as we would like to have a small plushie for the expo and since it will take time to produce it is required early on.
\\\\
The designers will be creating the keybinds for the game for both the keyboard and controller due to us integrating both into our game. They will also be collecting everyone's timetables in the group and mapping them on one another to determine the best time for daily meetings as well as general meetings due to a lack of communication in the team. Two lists will also be created which will detail the animations required as well as the particles required for the game and will be acted upon in later sprints. The GDD is also intended to be revised to ensure that it is informative as possible to all disciplines. Sound will also be looked into too and researched to ensure we are able to collect and implement it later down the line. The tutorial concept is also expected to be finished too to allow the writer to come up with the dialogue for it.
\\\\
The writer will be deciding the final game name along with our animator to ensure we have a name that is most appropriate for our game and target audience. Moreover, they will also be assisting the tutorial in terms of dialogue as aforementioned.
\\\\
Finally, our animator will start rigging the skeleton for our default generic character which will be used for most of the characters in our game. This is quite important due to its re-usability, so a fair amount of time should be spent on it.

\section{Tasks}
\subsection{Programmers}
\begin{itemize}
    \item Chris and James: General Refactoring of Code
    \item Chris: Movement and Pathfinding Integration
    \item James: Health System/Combat
    \item James: Unit Creation Kit
    \item James: Input Handler
    \item Chris: Camera Attributes
    \item James: Game UI Redone
\end{itemize}

\subsection{Modellers}
\begin{itemize}
    \item Liam P.: Scratching Post
    \item Liam P.: Cardboard Box
    \item Liam P.: Chairs
    \item Liam P.: Lamp
    \item Liam P.: Potted Plant
    \item Liam P.: Box Fort
    \item Alfie: Regular Cat Blockout
\end{itemize}

\subsection{Artists}
\begin{itemize}
    \item Naomi: Archer Concept Art
    \item Naomi: Spearman Concept Art
    \item Naomi: Plushie Concept Art
\end{itemize}

\subsection{Designers}
\begin{itemize}
    \item Deanna: Game Keybinds for Keyboard and Controller
    \item Deanna: Timetables Collected to determine best time for Daily Meetings
    \item Deanna: Animations Required List
    \item Iestyn: Particle Required List
    \item Naomi: GDD Revision
    \item Iestyn and Liam W.: Sound Research
    \item Lachezar: Tutorial Concept
    \item Chris: Sprint Master Plan
    \item Chris: Sprint 2 Plan
\end{itemize}

\subsection{Writers}
\begin{itemize}
    \item Liam W.: Final Game Name
    \item Liam W.: Dialogue for Tutorial
\end{itemize}

\subsection{Animators}
\begin{itemize}
    \item Summer: Default Character Skeleton Rigging
\end{itemize}


\end{document}